%Need to following so subdirectories can all find ALICE_analysis_note.cls and
%other files needed from main directory
\makeatletter
\def\input@path{{/home/jesse/Analysis/FemtoAnalysis/AnalysisNotes/}}
%or: \def\input@path{{/path/to/folder/}{/path/to/other/folder/}}
\makeatother

%\documentclass[ALICE,manyauthors]{ALICE_analysis_notes}
\documentclass[ALICE,manyauthors]{ALICE_analysis_notes}


%\documentclass[ALICE,manyauthors]{ALICE_scientific_notes}
%
%\newcommand{\jpsi}{\rm J/$\psi$}
%\newcommand{\psip}{$\psi^\prime$}
%\newcommand{\jpsiDY}{\rm J/$\psi$\,/\,DY}
%\newcommand{\dd}{\mathrm{d}}
%\newcommand{\chic}{$\chi_{\rm c}$}
%\newcommand{\ezdc}{$E_{\rm ZDC}$}
%\newcommand{\red}{\textcolor{red}}
%\newcommand{\blue}{\textcolor{blue}}
\newcommand{\slfrac}[2]{\left.#1\right/#2}
\usepackage{rotating}
\usepackage{comment} 
\usepackage{multirow}
\usepackage{subfiles}
\usepackage{morefloats}

\usepackage{subfig,graphicx}
\usepackage{epstopdf}
\usepackage{subfloat} %%need for subfigures, like Fig 5a, 5b, and 5c
\usepackage{amsmath}  %%need to make Eq 1 look pretty
\usepackage[font=small]{caption}
\captionsetup[subfigure]{margin=10pt,parskip=5pt,indention=10pt,singlelinecheck=false}

\usepackage{amsmath,amssymb}

\usepackage{color}	%May be necessary for colored links
\usepackage{hyperref}

\usepackage{pdflscape}

\usepackage{lineno}

\begin{comment}
\hypersetup{
    linktoc=all, %set to all for both sections and subsections linked
	colorlinks=true, %set true if you want colored links
	linkcolor=red, %choose some color for links
	anchorcolor=black,
	citecolor=green,
	filecolor=cyan,
	menucolor=red,
	runcolor=cyan,
	urlcolor=magenta
}
\end{comment}

\hypersetup{
	linktoc=all,
	colorlinks=false,
	linkbordercolor={1 0 0},
	citebordercolor={0 1 0},
	filebordercolor={0 .5 .5},
	menubordercolor={1 0 0},
	runbordercolor={0 .7 .7},	
	urlbordercolor={0 1 1}
}

%%%%%%%%%%%%% Shortcuts for writing particles and pairs %%%%%%%%%%%%%%%
\usepackage{xspace} %%Needed so there will be a space after the following commands!

\newcommand{\Lam}{$\Lambda$\xspace}
\newcommand{\ALam}{$\bar{\Lambda}$\xspace}

\newcommand{\KchP}{$\mathrm{K^{+}}$\xspace}
\newcommand{\KchM}{$\mathrm{K^{-}}$\xspace}
\newcommand{\Kpm}{$\mathrm{K^{\pm}}$\xspace}

\newcommand{\Ks}{$\mathrm{K^{0}_{S}}$\xspace}

\newcommand{\LamK}{$\Lambda$K\xspace}

\newcommand{\LamKchP}{$\Lambda\mathrm{K^{+}}$\xspace}
\newcommand{\ALamKchM}{$\bar{\Lambda}\mathrm{K^{-}}$\xspace}

\newcommand{\LamKchM}{$\Lambda\mathrm{K^{-}}$\xspace}
\newcommand{\ALamKchP}{$\bar{\Lambda}\mathrm{K^{+}}$\xspace}

\newcommand{\LamKpm}{$\Lambda\mathrm{K^{\pm}}$\xspace}
\newcommand{\ALamKpm}{$\bar{\Lambda}\mathrm{K^{\pm}}$\xspace}


\newcommand{\LamKs}{$\Lambda\mathrm{K^{0}_{S}}$\xspace}
\newcommand{\ALamKs}{$\bar{\Lambda}\mathrm{K^{0}_{S}}$\xspace}

\newcommand{\XiKchP}{$\Xi^{-}\mathrm{K^{+}}$\xspace}
\newcommand{\AXiKchM}{$\bar{\Xi}^{+}\mathrm{K^{-}}$\xspace}

\newcommand{\XiKchM}{$\Xi^{-}\mathrm{K^{-}}$\xspace}
\newcommand{\AXiKchP}{$\bar{\Xi}^{+}\mathrm{K^{+}}$\xspace}


\newcommand{\XiKpm}{$\Xi^{-}\mathrm{K^{\pm}}$\xspace}
\newcommand{\AXiKpm}{$\bar{\Xi}^{+}\mathrm{K^{\pm}}$\xspace}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%% Define various directories %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ResultsDir}{/home/jesse/Analysis/FemtoAnalysis/Results/}
\newcommand{\ResultsDirLamKch}{/home/jesse/Analysis/FemtoAnalysis/Results/Results_cLamcKch_20171227/}
\newcommand{\ResultsDirLamKs}{/home/jesse/Analysis/FemtoAnalysis/Results/Results_cLamK0_20171227/}


%
\begin{document}%
%%%%%%%%%%%%% ptdr definitions %%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{titlepage}
%
\PHnumber{ALICE-ANA-2016-xxx} 
\PHdate{\today}
%
%%% Put your own title + short title here:
\title{Lambda-Kaon and Cascade-Kaon Femtoscopy in Pb-Pb Collisions at $\sqrt{s_{NN}}=2.76$ TeV from the LHC ALICE Experiment}
\ShortTitle{$\Lambda$-K and $\Xi$-K Femtoscopy with ALICE}   % appears on right page headers
%
\author{Jesse T. Buxton$^{1}$}
\author{
1. Department of Physics, The Ohio State University, Columbus, Ohio, USA\\
}
\author{Email: jesse.thomas.buxton@cern.ch}
%
\ShortAuthor{ALICE Analysis Note 2016}      % appears on left page headers, do not change
%
\begin{abstract}

\begin{comment}
My abstract will be contained here.  The abstract will introduce my study and inform the reader about the content of this paper.  I will state the problem I tackle, and summarize (in one sentence) why no one else has yet to adequately answered the research question.  Next, I will explain (again, in one sentence) how I tackled the research question, and (in one sentence) how I went about doing the research which followed from this big idea (i.e. elaborate on previous sentence).  Finally, as a single sentence, I will state the key impact of my research.
\end{comment}

\linenumbers

We present results from a femtoscopic analysis of Lambda-Kaon correlations in Pb-Pb collisions at $\sqrt{s_{NN}}$ = 2.76 TeV by the ALICE experiment at the LHC.  
All pair combinations of $\Lambda$ and $\bar{\Lambda}$ with K$^{+}$, K$^{-}$ and K$^{0}_{S}$ are analyzed.  
The femtoscopic correlations are the result of strong final-state interactions, and are fit with a parametrization based on a model by R. Lednicky and V. L. Lyuboshitz \cite{Lednicky:82}.  
This allows us to both characterize the emission source and measure the scattering parameters for the particle pairs.  
We observe a large difference in the \LamKchP (\ALamKchM) and $\Lambda$-K$^{-}$ ($\bar{\Lambda}$-K$^{+}$) correlations in pairs with low relative momenta (k$^{*}$ $\lesssim$ 100 MeV).  
Additionally, the average of the $\Lambda$-K$^{+}$ ($\bar{\Lambda}$-K$^{-}$) and $\Lambda$-K$^{-}$ ($\bar{\Lambda}$-K$^{+}$) correlation functions is consistent with our $\Lambda$-K$^{0}_{S}$ ($\bar{\Lambda}$-K$^{0}_{S}$) measurement.  
The results suggest an effect arising from different quark-antiquark interactions in the pairs, i.e. $\rm s\bar{s}$ in $\Lambda$-K$^{+}$ ($\bar{\Lambda}$-K$^{-}$) and $\rm u\bar{u}$ in $\Lambda$-K$^{-}$ ($\bar{\Lambda}$-K$^{+}$).  
To gain further insight into this hypothesis, we currently are conducting a $\Xi$-K femtoscopic analysis.
\end{abstract}
\end{titlepage}
%
%\input{alice_mynote.tex}               %%%%%%%%%%% put the body of the article here
%\input{0_Contents.tex}
\subfile{0_Contents.tex}
\clearpage
\bibliographystyle{unsrt}
\bibliography{bibfile}
\end{document}
