\documentclass[../AnalysisNoteJBuxton.tex]{subfiles}
\begin{document}

\subsection{Systematic Errors: \texorpdfstring{$\Xi$K$^{\pm}$}{TEXT}}
\label{SysErrsXiKch}

\subsubsection{Particle and Pair Cuts}
\label{SysErrsXiKch:ParticleAndPairCuts}

The cuts included in the systematic study, as well as the values used in the variations, are listed below.  Note, the central value corresponds to that used in the analysis.

\begin{enumerate}
 \item Max. DCA $\Xi$($\bar{\Xi}$): \{x, y, z mm\}
 \item Max. DCA $\Xi$($\bar{\Xi}$) Daughters: \{x, y, z mm\}
 \item Min. $\Xi$($\bar{\Xi}$) Cosine of Pointing Angle to Primary Vertex: \{0.9991, 0.9992, 0.9993\} 
 \item Min. $\Lambda$($\bar{\Lambda}$) Cosine of Pointing Angle to $\Xi$($\bar{\Xi}$) Decay Vertex: \{0.9992, 0.9993, 0.9994\} 
 \item Min. DCA Bachelor $\pi$: \{0.2, 0.3, 0.4 mm\}
 \item Min. DCA $\Lambda$($\bar{\Lambda}$): \{0.5, 1, 2 mm\}
 \item Max. DCA $\Lambda$($\bar{\Lambda}$) Daughters: \{3, 4, 5 mm\}
 \item Min. $\Lambda$($\bar{\Lambda}$) Cosine of Pointing Angle To Primary Vertex: \{0.9992, 0.9993, 0.9994\}
 \item Min. DCA to Primary Vertex of $p$($\bar{p}$) Daughter of $\Lambda$($\bar{\Lambda}$):  \{0.5, 1, 2 mm\}
 \item Min. DCA to Primary Vertex of $\pi^{-}$($\pi^{+}$) Daughter of $\Lambda$($\bar{\Lambda}$):  \{2, 3, 4 mm\} 
 \item Min. Average Separation of $\Lambda$($\bar{\Lambda}$) Daughter and K$^{\pm}$ with like charge: \{7, 8, 9 cm\}
 \item Min. Average Separation of Bachelor $\pi$ and K$^{\pm}$ with like charge: \{x, y, z cm\}
 \item Max. DCA to Primary Vertex in Transverse Plane of K$^{\pm}$: \{1.92, 2.4, 2.88\}
 \item Max. DCA to Primary Vertex in Longitudinal Direction of K$^{\pm}$: \{2.4, 3.0, 3.6\}
\end{enumerate}

\subsubsection{Non-Flat Background}
\label{SysErrsXiKch:NonFlatBgd}

Still needs to be done.  Currently, we fit our non-flat background with a linear function.  We will also use a quadratic form, and analyze how this choice affects our extracted parameter sets.

\subsubsection{Fit Range}
\label{SysErrsXiKch:FitRange}

Our choice of $k^{*}$ fit range was varied by $\pm$ 25\%.  The resulting uncertainties in the extracted parameter sets were combined with our uncertainties arising from our particle and pair cuts.

\end{document}